Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-03-14 SI.tex
Modification on 20190314

Here we will show the results of dielectric properties calculated
using many-body Green function method (G$_0$W$_{0}$)
and with electron-hole interactions at the level of the Bethe-Salpeter 
equation (G$_0$W$_{0}$--BSE). We first compare the case of a
monolayer of BN within a varying superlattice $L$ 
calculated using PBE and G$_{0}$W$_{0}$ as shown in Figure \ref{fig:GW-PBE-alpha}. 
%
%
Both $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ do not converge as a function of $L$ 
despite of the separation utilized in the simulations (Figure \ref{fig:GW-PBE-alpha}{\bf a}-{\bf c}). However, corresponding 2D polarizabilities are almost $L$-independent (Figure \ref{fig:GW-PBE-alpha}{\bf b}-{\bf d}). It is worth noting
that since the G$_{0}$W$_{0}$ method has better estimation of the bandgap, $\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller using G$_{0}$W$_{0}$ than in PBE functionals.
\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
 \caption{{\bf Variation of 
   $\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for
   monolayer BN calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.}
   \textbf{a}-{\bf b}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\parallel}$ as function of $L$, respectively.    
  \textbf{c}-{\bf d}. $\varepsilon_{\mathrm{SL}}^{\perp}$ and 
  $\alpha_{\mathrm{2D}}^{\perp}$ as
   function of $L$. 
   In all cases the values obtained using
   G$_{0}$W$_{0}$ method is smaller than that using PBE method due to
   better estimation of the bandgap.}
  \label{fig:GW-PBE-alpha}
\end{figure}

@@

We calculate the frequency-dependent dielectric properties of BN with
varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$--BSE. 
Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out} show the
magnitudes of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
$\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
throughout the whole frequency range at PBE level. The $L$-dependency can also be
removed using main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, yielding lattice-independent
polarizabilities throughout the frequency domain (Figure \ref{fig:PBE-omega-in}{\bf b}-{\bf d} and \ref{fig:PBE-omega-out}{\bf b}-{\bf d}). 
%
Note that when extracting the frequency-dependent 2D polarizabilities
from main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, the peak position in energy
$\hbar \omega$ from $\varepsilon_{\mathrm{SL}}$ is preserved. This is
explained by the fact that the local extrema from spectra of
$\varepsilon_{\mathrm{SL}}$ is also the local extrema in corresponding
$\alpha_{\mathrm{2D}}$, since when
$\partial \varepsilon_{\mathrm{SL}}(\omega) / \partial \omega = 0 $,
we have
\begin{subequations}
\begin{eqnarray}
  \label{eq:extrema-para}
  \frac{\partial \alpha_{\mathrm{2D}}^{\parallel}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0   \\
  \label{eq:extrema-perp}
  \frac{\partial \alpha_{\mathrm{2D}}^{\perp}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{2}}\frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0
\end{eqnarray}
\end{subequations}
which indicates that no corrections in energy are present 
when transforming
$\varepsilon_{\mathrm{SL}}(\omega)$ to $\alpha_{\mathrm{2D}}(\omega)$.
Performing the simulations at the level of G$_{0}$W$_{0}$
we observe shifts in energy in $\varepsilon_{\mathrm{SL}}(\omega)$ 
as a function of $L$. Figures \ref{fig:GW-omega-in} and
\ref{fig:GW-omega-out} show that not only the magnitude of the dielectric
functions change with $L$ but also the peak positions. As a result
the obtained polarizabilities also show $L$-dependent peak 
shift (Figures \ref{fig:GW-omega-in} {\bf b}-{\bf d} and
\ref{fig:GW-omega-out}{\bf b}-{\bf d}). This
can be explained by the long-range nature of Coulomb interactions into the self-energy 
$\Sigma=iGW$.

@@

Due to the volume dependence of $\Sigma$ in equations \ref{self} and
\ref{quasi}, increasing the vacuum spacing leads to a change in the
calculated quasi-particle eigenergies. This, along with the volume
dependence in the calculation of the dielectric function, leads to an
increase in energy of the peak position and a decrease in its
magnitude with increasing vacuum spacing.  Including excitonic effects
on top of a G$_0$W$_0$ calculation through solving the Bethe--Salpeter
equation corrects for this energy shift by localizing the exciton
within the slab (Figures \ref{fig:BSE-omega-in} and
\ref{fig:BSE-omega-out}). However, the decrease in the magnitude of
the dielectric function on both components of
$\varepsilon_{\mathrm{SL}}(\omega)$ with increasing vacuum spacing is
still observed.  Using main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def} we can remove the dependence on $L$ as
plotted in Figures \ref{fig:BSE-omega-in}{\bf b}-{\bf d} and
\ref{fig:BSE-omega-out}{\bf b}-{\bf d} with few variations on
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$.

@@

\pagebreak{}
\section{Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant}
\label{sec:2D-3D-rescale}
From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric
constant of the superlattice, where the layers are periodic along of
x,y directions but separated by a vacuum layer between its images
\cite{Matthes_2016,Laturia_2018}. As discussed in the main text, the
definition of the 2D ``dielectric constant'' (in particular, its
in-plane components) is questionable, due to the locality of
electrostatic screening of the 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Here we show
that, in addition to the ambiguous definition of the 2D dielectric
constant, such approach requires the precise determination of the 2D
layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical.

In brief, the hypothetical 2D dielectric constant
$\varepsilon$ comes from the planar limit of the
Maxwell-Garnett effective medium theory \cite{Markel_2016}, and can be
expressed by means of the macroscopic dielectric constant
$\varepsilon_{\mathrm{SL}}$ of the superlattice:

@@

Another drawback of the 2D dielectric constant approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{eq:MG-effect-1} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}

@@

To conclude, based on theoretical and technical considerations, there are several
advantages of using the polarizability $\alpha$ for describing the dielectric
nature of 2D materials, including
\begin{enumerate}
\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
\item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.

\item The value of $\epsilon_{\mathrm{2D}}$ hugely depends on the
  choice of the thickness of 2D material, while such information is
  intrinsically embedded in $\alpha_{\mathrm{2D}}$.
\end{enumerate}

>>>>

Here we will show the results of dielectric properties calculated
using many-body Green function method (G$_0$W$_{0}$) and with
electron-hole interactions at the level of the Bethe-Salpeter equation
(G$_0$W$_{0}$--BSE). Frequency-dependent dielectric functions
$\varepsilon_{\mathrm{SL}}(\omega)$ at both G0W0 and G0W0--BSE levels
are calculated using VASP, with a cutoff energy of XXX and k point
density of YYY. Local field effect is included in both cases: local
field correction is applied to independent-particle energies in G0W0
at RPA level with VASP TAG \texttt{LRPA=.TRUE.}, while the full
polarizability is calculated using BSE in G0W0-BSE
\todo[inline]{@Declan, could you help modify this part?}

We first compare the case of a monolayer of BN within a varying
superlattice $L$ calculated using PBE and G$_{0}$W$_{0}$ as shown in
Figure \ref{fig:GW-PBE-alpha}.  Both
$\varepsilon_{\mathrm{SL}}^{\parallel}$ and
$\varepsilon_{\mathrm{SL}}^{\perp}$ do not converge as a function of
$L$ despite of the separation utilized in the simulations (Figure
\ref{fig:GW-PBE-alpha}{\bf a}-{\bf c}). However, corresponding 2D
polarizabilities are almost $L$-independent (Figure
\ref{fig:GW-PBE-alpha}{\bf b}-{\bf d}). It is worth noting that since
the G$_{0}$W$_{0}$ method has better estimation of the bandgap,
$\varepsilon_{\mathrm{SL}}$ and $\alpha_{\mathrm{2D}}$ are smaller
using G$_{0}$W$_{0}$ than in PBE functionals.
\begin{figure}[htbp]
  \centering
 \includegraphics[width=0.9\linewidth]{img/SI-GW-alpha-zero.pdf}
 \caption{{\bf Variation of 
   $\varepsilon^{\perp}_{\mathrm{SL}}$ as a function of $L$ for
   monolayer BN calculated at the level of PBE and G$_{\rm 0}$W$_{0}$.}
   \textbf{a}-{\bf b}. $\varepsilon_{\mathrm{SL}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\parallel}$ as function of $L$, respectively.    
  \textbf{c}-{\bf d}. $\varepsilon_{\mathrm{SL}}^{\perp}$ and 
  $\alpha_{\mathrm{2D}}^{\perp}$ as
   function of $L$. 
   In all cases the values obtained using
   G$_{0}$W$_{0}$ method is smaller than that using PBE method due to
   better estimation of the bandgap.}
  \label{fig:GW-PBE-alpha}
\end{figure}

@@

We calculate the frequency-dependent dielectric properties of BN with
varying supperlattice $L$ at PBE, G$_{0}$W$_{0}$, and G$_{0}$W$_{0}$--BSE. 
Figure \ref{fig:PBE-omega-in} and \ref{fig:PBE-omega-out} show the
magnitudes of $\varepsilon_{\mathrm{SL}}^{\parallel}(\omega)$ and
$\varepsilon_{\mathrm{SL}}^{\perp}(\omega)$ reduce with increasing $L$
throughout the whole frequency range at PBE level. The $L$-dependency can also be
removed using main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, yielding lattice-independent
polarizabilities throughout the frequency domain (Figure \ref{fig:PBE-omega-in}{\bf b}-{\bf d} and \ref{fig:PBE-omega-out}{\bf b}-{\bf d}). 
%
Note that when extracting the frequency-dependent 2D polarizabilities
from main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def}, the peak position in energy
$\hbar \omega$ from $\varepsilon_{\mathrm{SL}}$ is preserved. This is
explained by the fact that the local extrema from spectra of
$\varepsilon_{\mathrm{SL}}$ is also the local extrema in corresponding
$\alpha_{\mathrm{2D}}$, since when
$\partial \varepsilon_{\mathrm{SL}}(\omega) / \partial \omega = 0 $,
we have
\begin{subequations}
\begin{eqnarray}
  \label{eq:extrema-para}
  \frac{\partial \alpha_{\mathrm{2D}}^{\parallel}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0   \\
  \label{eq:extrema-perp}
  \frac{\partial \alpha_{\mathrm{2D}}^{\perp}(\omega)}{\partial \omega}
  &= \varepsilon_{0}L {\displaystyle \frac{1}{\varepsilon_{\mathrm{SL}}^{2}}\frac{\partial \varepsilon_{\mathrm{SL}}^{\parallel}}{\partial \omega}} = 0
\end{eqnarray}
\end{subequations}
which indicates that no corrections in energy are present 
when transforming
$\varepsilon_{\mathrm{SL}}(\omega)$ to $\alpha_{\mathrm{2D}}(\omega)$.
Performing the simulations at the level of G$_{0}$W$_{0}$
we observe blue shifts in energy in $\varepsilon_{\mathrm{SL}}(\omega)$ 
with increasing $L$. Figures \ref{fig:GW-omega-in} and
\ref{fig:GW-omega-out} show that not only the magnitude of the dielectric
functions change with $L$ but also the peak positions. As a result
the obtained polarizabilities also show $L$-dependent peak 
shift (Figures \ref{fig:GW-omega-in} {\bf b}-{\bf d} and
\ref{fig:GW-omega-out}{\bf b}-{\bf d}). This
can be explained by the long-range nature of Coulomb interactions into the self-energy 
$\Sigma=iGW$.

@@

Due to the volume dependence of $\Sigma$ in equations \ref{self} and
\ref{quasi}, increasing the vacuum spacing leads to a change in the
calculated quasi-particle eigenergies. This, along with the volume
dependence in the calculation of the dielectric function, leads to an
increase in energy of the peak position and a decrease in its
magnitude with increasing vacuum spacing. Such effect is also
discussed in several other studies
\cite{Rozzi_2006,Hueser_2013_2Dvs3D}, when full Coulomb interaction is
used in a supercell. Including excitonic effects on top of a
G$_0$W$_0$ calculation through solving the Bethe--Salpeter equation
corrects for this energy shift by localizing the exciton within the
slab (Figures \ref{fig:BSE-omega-in} and
\ref{fig:BSE-omega-out}). However, the decrease in the magnitude of
the dielectric function on both components of
$\varepsilon_{\mathrm{SL}}(\omega)$ with increasing vacuum spacing is
still observed.  Using main text Eqs. \ref{main-eq:alpha-para-def} and
\ref{main-eq:alpha-perp-def} we can remove the dependence on $L$ as
plotted in Figures \ref{fig:BSE-omega-in}{\bf b}-{\bf d} and
\ref{fig:BSE-omega-out}{\bf b}-{\bf d} with fewer variations on
$\varepsilon^{\perp}_{\mathrm{SL}}(\omega)$.

@@

\pagebreak{}
\section{Comment on the hypothetical ``dielectric constant'' in the effective medium theory (EMT)}
\label{sec:2D-3D-rescale}
From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric
constant of the superlattice, where the layers are periodic along of
x,y directions but separated by a vacuum layer between its images
\cite{Matthes_2016,Laturia_2018}. Such method makes use of the
effective medium theory (EMT), and as discussed in the main text, the
definition of the 2D ``dielectric constant'' is questionable, due to
the locality of electrostatic screening of the 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Moreover, the
EMT approach assumes that the 2D material has an effective thickness
$\delta$ and effective dielectric constant
$\varepsilon_{\mathrm{2D}}$, while the exact value of $\delta$ is
unknown due to the ambiguity of the reference planes. Here we show
that, in addition to the ambiguous definition of the 2D dielectric
constant, such approach requires the precise determination of the 2D
layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical. On
the contrary, the 2D polarizability approach presented in the main
text is independent of the choice of the parameter $\delta$, as well
as the volume fraction of the 2D material, and can correctly capture
the dielectric properties of the 2D material.

In brief, the hypothetical 2D dielectric constant
$\varepsilon$ comes from the planar limit of the
effective medium theory \cite{Markel_2016,Aspnes_1982}, and can be
expressed by means of the macroscopic dielectric constant
$\varepsilon_{\mathrm{SL}}$ of the superlattice:

@@

Another drawback of the 2D EMT approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{eq:MG-effect-1} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}

@@

To conclude, based on theoretical and technical considerations, there are several
advantages of using the polarizability $\alpha$ for describing the dielectric
nature of 2D materials, including
\begin{enumerate}
\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ in EMT requires calculation with varied superlattice length.
\item $\alpha_{\mathrm{2D}}$ correctly represents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.
\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ calculated from EMT does not.

\item The value of $\epsilon_{\mathrm{2D}}$ in EMT hugely depends on the
  choice of the thickness of 2D material, while such information is
  intrinsically embedded in $\alpha_{\mathrm{2D}}$.
\end{enumerate}

### 2019-03-14 paper.tex
Modification on 20190314

(EMT) treatment\cite{Aspnes_1982} of 2D materials, in which the
hypothetical effective dielectric constant of 2D materials

@@

meaning. Detailed discussions can be found in Supplementary Section
\ref{SI-sec:2D-3D-rescale}.

>>>>

\cite{Aspnes_1982,Markel_2016} (EMT) treatment of 2D materials, in
which the hypothetical effective dielectric constant of 2D materials

@@

meaning. Detailed discussions about the different between the 2D
polarizability and the EMT approach, can be found in Supplementary
Section \ref{SI-sec:2D-3D-rescale}.
